\begin{frame}{Biblio Radiative transfer}
$\S$ Mihalas
– "Stellar Atmospheres" (1970) (?)
– "Stellar Atmospheres" (1978) (*)
– with Hubeny ́: "Theory of Stellar Atmospheres" (2014)
$\S$ simpler
– Novotny: "Introduction to stellar atmospheres and interiors" (1973)
– Gray: "The observation and analysis of stellar photospheres" (2005) – Bo ̈hm-Vitense: "Introduction to stellar astrophysics I, II" (1989)
$\S$ harder
– Cannon: "The transfer of spectral line radiation" (1985)
– Mihalas & Mihalas: "Foundations of Radiation Hydrodynamics" (1984) (*) – Castor: "Radiation Hydrodynamics" (2004)
$\S$ my stuff
– IART: bachelors-level radiative transfer (1991, 2015, 20??) (*)
– RTSA: masters-level Mihalas popularization (2003, 20??) (*)
– ISSF: bachelors-level introduction to NLTE (1993) (*)
– Monterey: PhD-level refresher NLTE chromospheric lines for IRIS (2012) (*) – Cartagena: tutorial non-E hydrogen diagnostics for ALMA (2016) (*)
\end{frame}

\begin{frame}[allowframebreaks]{Reg Lez (rec)}

\begin{itemize}
\item 4 Ottobre. P cygni spectrum: frobbidden/permitted lines, broadening, shock, autoionization, velocity gradient.
LTE, coupling rules, line ratio (ration intensity members of multiplets),

 map wavelength to pixels, Stati atomici,
\item 8 ottobre. (Processi) armonic oscillator one characteristic frequency-planck function used in E. coefficient  (TE);broaden due to spontaneous decay: $A\propto\Gamma$. Lorentzian profile. Complete redistribution: efficience of absorption do not affect re-emission.
Seeing through optical thin medium sampling different temperature. Rotational profile. Voigt profile $H(\frac{\Delta\omea}{\Delta\omega_D},\frac{\Gamma}{\Delta\omega_D})=H(v,a)$. Equivalent width (line). Regime in cui le ali sono trascurabili: small a. Curve of growth.
\item 9 Ott (Osservativa). Colori: Bande fotometriche Johnson, Str\:omgren. Interferenza: separazione ordine (dispersion). Fotometria: opacit\'a atmosfera vs spazio; osservazione relative da Terra (bootstrapping) (?MK system); plate vs CCD; Vega vs AB-mag. Atmosfera: real/immaginary part of extintion; horizon problem; fluctuation of index of refraction (seeing): lunghezza di coerenza, turbulence. PSF: Gaussian (uncorrelate fluctuation). RA/DEC and field rotation.

\item Lun mart: resonant de-excitation, molecules

\item 18 Ottobre. CCD; low resolution spectra; strumental noise (temerature), ...
Frank-condon factor; molecular reaction
thermal electric fluctuation
\item 29 ottobre. Frank-Condon facor. Electron configuration in molecules. H molecular almost transparent. Radiative transfer; atmosphere: albedo, radiative equilibrium, atmosphere, star wind.
continuum media vs cosmological conditions: 21cm line
\item 30 ottobre. Astrofisica: come si passa da descrizione miscroscopica a macroscopica? (galaxies-fluid + poisson eq); collisional/less: momentum transfer, kinetic (dis)equilibrium, E/L description (c.e.). Coupling between mass, momentum, energy conservation: hierarchy of momenta. Duck Lion. Intro to turbulence. Stress tensor: shear is the non-diagonal term. Shock: discontinuity surface (spatial scale go to zero). continuous conditions across shock: shock adiabat ($\^$). Discontinuity: casello dove la densit\'a dopo \'e minore di quella prima. How we can define T after shock front passage. Precursor. Ionization front, Str\"omgren sphere. 
\end{itemize}

\end{frame}